noam_data_exploration_v1

### 2024-07-22 noam_data_exploration_v3.Rmd
Continuing to add more vis options.

@@

diversity_stability_quadrat <- 
  merge(diversity_stability_quadrat, lm_synchrony_quadrat, by = "Location") # add in loreau and de Mazancourt synchrony
diversity_stability_quadrat <- merge(diversity_stability_quadrat, gross_synchrony_quadrat, by = "Location")
diversity_stability_quadrat <- merge(diversity_stability_quadrat, quadrat_level_portfolio, by = "Location") # add in portfolio effects
pairs(~ Cover_mean + Cover_cv + Cover_stability + 
        Shannon_mean + Shannon_cv + Shannon_stability + 
        Loreau_synchrony + Gross_synchrony + Portfolio_effect, data = diversity_stability)

@@

```{r basic diversity stability plots quadrat level, fig.height=8, fig.width=10}
(shannon_cv_plot = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = Shannon_mean, y = Cover_cv, colour = Site, shape = Habitat), size = 8) + 
   scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
#    stat_smooth(aes(x = Shannon_mean, y = Shannon_cv),method = "lm", se = T, size = 2) + 
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r portfolio effects and synchrony transect level,  fig.height = 8, fig.width = 10}
(loreau_stability_plot_quad = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = Loreau_synchrony, y = Cover_cv, colour = Site, shape = Habitat), size = 4, stroke = 1) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Habitat) +

@@

(portfolio_stability_plot_quad = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = Portfolio_effect, y = Cover_cv, colour = Site, shape = Habitat), size = 4, stroke = 2) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site) +

```{r diversity portfolio effects and synchrony quadrat level,  fig.height = 8, fig.width = 10}
(loreau_diversity_plot_quad = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = Shannon_mean, y = Loreau_synchrony, colour = Site, shape = Habitat), size = 4, stroke = 1) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Habitat) +

>>>>

variance_ratio_quadrat <- variance_ratio(df = long_data_sub,
                                   time.var = "Year",
                                   species.var = "Taxa",
                                   abundance.var = "Percent_cover",
                                   average.replicates = F,
                                   bootnumber = 1,
                                   replicate.var = "Location")

@@

diversity_stability_quadrat <- 
  merge(diversity_stability_quadrat, lm_synchrony_quadrat, by = "Location") # add in loreau and de Mazancourt synchrony
diversity_stability_quadrat <- merge(diversity_stability_quadrat, gross_synchrony_quadrat, by = "Location")
diversity_stability_quadrat <- merge(diversity_stability_quadrat, quadrat_level_portfolio, by = "Location") # add in portfolio effects
diversity_stability_quadrat <- merge(diversity_stability_quadrat, variance_ratio_quadrat, by = "Location")
pairs(~ Cover_mean + Cover_cv + Cover_stability + 
        Shannon_mean + Shannon_cv + Shannon_stability + 
        Loreau_synchrony +  Portfolio_effect + VR, data = diversity_stability_quadrat)

@@

```{r basic diversity stability plots quadrat level, fig.height=8, fig.width=10}
(shannon_cv_plot = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = Shannon_mean, y = Cover_cv, colour = Site, shape = Habitat), size = 4) + 
   scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
   facet_wrap(~Site) +

@@

```{r portfolio effects and synchrony transect level,  fig.height = 8, fig.width = 10}
(loreau_stability_plot_quad = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = Loreau_synchrony, y = Cover_cv, colour = Site, shape = Habitat), size = 4, stroke = 1) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site) +

@@

(portfolio_stability_plot_quad = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = Portfolio_effect, y = Cover_cv, colour = Site, shape = Habitat), size = 4, stroke = 2) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
 # facet_wrap(~Site) +

  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         ) # almost a perfect line, which makes sense given that CV is a component of portfolio effects

```{r diversity portfolio effects and synchrony quadrat level,  fig.height = 8, fig.width = 10}
(loreau_diversity_plot_quad = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = Shannon_mean, y = Loreau_synchrony, colour = Site, shape = Habitat), size = 4, stroke = 1) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site) +
